### 2017-03-20 Manuscripts/cog-psych/cogpsych.tex
update prior to joes lookover

@@

In the sections below, we report simulations using this copy-and-tweak model.  Due to their mathematical equivalence, the comparison between PACKER and copy-and-tweak provides a test of the explanatory value of the contrast mechanism: the account provided by copy-and-tweak will only equal that of PACKER if the contrast mechanism does not offer an advantage.

@@

To simplify the model predictions, we used {\em maximum a posteriori} (MAP) estimates for the hidden parameters and then generated new categories based on those estimates. Due to conjugacy, the MAP estimate for the shared covariance matrix $\Sigma_D = \Sigma_0 + \sum_c{C_c}$, where $C_c$ is the empirical covariance matrix of category $c$. The MAP estimate of the covariance matrix for the target category $B$ is 
\begin{equation}
  \Sigma_B = \left[ \Sigma_D \nu + C_B +
    \dfrac
    {\kappa n_B}
    {\kappa + n_B}
    (\bar{x_B}-\mu_B)(\bar{x_B}-\mu_B)^T
  \right] (\nu + n_B)^{-1}
  \label{eq:Sigma_B}
\end{equation}
%
where $\nu$ ($\nu>k-1$) is an additional free parameter (from the Inverse-Wishart prior on $\Sigma_B$) weighting the importance of $\Sigma_{D}$. When the target category has no members (i.e., $n_B = 0$), items are generated at random.

>>>>

\begin{figure}
    \begin{center}
    \input{figs/e2-conditions.pgf}
    \caption{Category types tested in Experiment 2.}
    \label{fig:e2-conditions}
    \end{center}
\end{figure}

We developed two Alpha categories (see Figure \ref{fig:e2-conditions}): the `Bottom' category is a tight cluster in the bottom-center of the space, and the `Middle' category is identical except that it lies in the center of stimulus space. Although this manipulation is minimal (the conditions differ only slightly in the Y-axis position of the experimenter-defined category), the PACKER model predicts strong between-condition differences. According to PACKER, the nature of the space not occupied by the existing categories should determine where members of the Beta category are likely to be generated. Thus, the lower areas of the stimulus space should be less frequently used for generation in the Bottom condition compared to the Middle (as these areas possess greater similarity to the Bottom category). Conversely, the upper areas of the stimulus space should be used for generation more frequently in the Bottom condition compared to Middle.

@@

In this paper, we report simulations using this copy-and-tweak model. The model we test is identical to PACKER, under the constraints that $\phi = 0$ and $\gamma = 1$, and is a continuous-dimension adaptation of the model tested by \cite{jern2013probabilistic}. Due to their mathematical equivalence, the comparison between PACKER and copy-and-tweak provides a test of the explanatory value of the contrast mechanism: the account provided by copy-and-tweak will only equal that of PACKER if the contrast mechanism does not offer an advantage.

@@

To simplify the model predictions, we used {\em maximum a posteriori} (MAP) estimates for the hidden parameters and then generated new categories based on those estimates. Due to conjugacy, the MAP estimate for the shared covariance matrix $\Sigma_D = \Sigma_0 + \sum_c{C_c}$, where $C_c$ is the empirical covariance matrix of category $c$. The MAP estimate of the covariance matrix for the target category $B$ is 
\begin{equation}
  \Sigma_B = \left[ \Sigma_D \nu + C_B +
    \dfrac
    {\kappa n_B}
    {\kappa + n_B}
    (\bar{x}_B-\mu_B)(\bar{x}_B-\mu_B)^T
  \right] (\nu + n_B)^{-1}
  \label{eq:Sigma_B}
\end{equation}
%
where $\nu$ ($\nu>k-1$) is an additional free parameter (from the Inverse-Wishart prior on $\Sigma_B$) weighting the importance of $\Sigma_{D}$. When the target category has no members (i.e., $n_B = 0$), items are generated at random.

\nbcnote{should explain Equation \ref{eq:Sigma_B} more fully now that we are not limited for space.}
